### 2013-11-18 paper/paper.tex
Changed width of figure
changed width of figure
added potential future work
Added description to figure

\documentclass[11pt,twoside,a4paper]{article}
\usepackage{amssymb, amsmath,graphicx,soul,color}

@@

\subsection{Traditional Measures}
TODO Describe in a few paragraphs each of the following metrics ...

@@

\hl{TODO: this is where you put your figure and discription}

\begin{figure}[h!]
  \centering
   \includegraphics[width=1\textwidth]{change_complexity_figure}
   \caption{"Change Complexity vs. Traditional Complexity"}
\end{figure}

@@

>>>>

\documentclass[8pt,twocolumn,a4paper]{article}
\usepackage{amssymb, amsmath,graphicx,soul,color}

@@

\subsection{Traditional Complexity Measures}

@@

In figure 1 we illustrate a hypothetical system which undergoes numerous changes. The vertical lines represent each version. During each version's development, the change complexity measures are assessed. In between versions, traditional complexity measures are computed. These are denoted by CCM and TCM respectively.

\begin{figure}[h!]
  \centering
 %  \includegraphics[width=0.5\textwidth]{change_complexity_figure}
   \caption{"Change Complexity vs. Traditional Complexity"}
\end{figure}

\begin{equation}
{{CCM_{v}(i)} \sim {TCM_{v(i+1)}}-{TCM_{v(i)}}}
\end{equation}

\begin{equation}
{{TCM_{v(i+1)}} \sum\limits_{i=0}^iCCM_{v(i)}}
\end{equation}

@@

Future work: Does McCabe predict anything? Do the change complexity measures do a better job of prediction?
